ABC_cichlids

### 2025-03-10 application_examples/abc_inferences/ABC_cichlids.Rmd
Updating to test new sumstats with ABC
Implemented modification to approximate cftp after a given step limit, pending testing

```{r load params and sumstats}
load("design.RData")
names(sampled_params)[12] <- "TMRCA_smallestCherry"
load("merged_sumStats.RData")
```

@@

@@

>>>>

```{r load params and sumstats}
load("design.RData")
names(sampled_params)[12] <- "TMRCA_smallestCherry"
load("merged_sumStats_old.RData")
```

@@

#### mu

@@

#### TMRCA

```{r}
hist(params$TMRCA_smallestCherry)
```

```{r}
summary(params$TMRCA_smallestCherry)
```

```{r}
plot(params$TMRCA_smallestCherry,
     merged_sumStats$MeanSiteFChange_i)
```

```{r}
plot(params$TMRCA_smallestCherry,
     merged_sumStats$MeanSiteFChange_ni)
```

```{r}
estim <- loclinear_cv$estim$tol0.01[,"TMRCA_smallestCherry"]
param <- loclinear_cv$true[,"TMRCA_smallestCherry"]
(1/100)*sum(abs(estim-param)/param)
```
```{r}
estim <- loclinear_cv$estim$tol0.01[,"mu"]
param <- loclinear_cv$true[,"mu"]
(1/100)*sum(abs(estim-param)/param)
```

### 2025-03-10 application_examples/abc_inferences/ABC_cichlids_new.Rmd
Implemented modification to approximate cftp after a given step limit, pending testing

```{r load params and sumstats}
load("design.RData")
names(sampled_params)[12] <- "TMRCA_smallestCherry"
load("merged_sumStats_old.RData")
```

@@

@@

```{r}
plot(expIWE_perIsland, merged_sumStats$Fitch_islandGlbSt)
```

@@

>>>>

```{r load params and sumstats}
load("design.RData")
names(sampled_params)[12] <- "TMRCA_smallestCherry"
load("merged_sumStats.RData")
```

@@

## Params as Exp Value and SD. Log scale

```{r}
transf <- c("log", "none", "log", rep("none", 9))
names(transf) <- names(params_expSD)
transf
```

```{r}
set.seed(1)
loclinear_cv <- cv4abc(params_expSD, merged_sumStats,
                       nval = 100,
                       method = "loclinear",
                       transf = transf,
                       tols = 0.01)
set.seed(1)
ridge_cv <- cv4abc(params_expSD, merged_sumStats,
                   nval = 100, 
                   method = "ridge",
                   transf = transf,
                   tols = 0.01)
```

@@

```{r}
plot(expIWE_perIsland, merged_sumStats$cherryFreqsChange_i,
     main = "cherryFreqsChange")
```

```{r}
plot(expIWE_perIsland, merged_sumStats$treeFreqsChange_i,
     main = "cherryFreqsChange")
```

@@

## New prior to try for alpha_Ri
```{r}
load("design.RData")
hist(sampled_params$alpha_Ri) # old

```
```{r}
hist(rexp(10000, 0.1), 50) #new
```

```{r}

```
